---
title: "dogmar: A guide"
author: s253700, s253704, s253699, s253694, s253696
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{dogmar: A guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

::: {style="text-align: center;"}
# DogmaR User guide
:::

**GitHub Repository:** [dogmar](https://github.com/rforbiodatascience25/group_04_package)

```{r, include = FALSE}
# 
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**Package description** It is a package that allows you to translate a randomly generated DNA sequence into proteins. It also allows you to perform a brief analysis of protein composition.

```{r setup}
library(dogmar)
```

::: {style="text-align: center;"}
## Functions
:::

## create_dna(length)

This function creates a random DNA sequence of a specific length determined by the parameter "length" Argument:

-   length: Specify the length of the output random DNA sequence

```{r}
dna <- create_dna(50)
print(f"The randomly generated DNA sequence is: {dna}")
print(f"The length of the DNA sequence is:{len(dna)}")
print(len(dna))
```

## to_rna(dna)

This function takes a DNA sequence as input and converts it into the corresponding RNA sequence by replacing all occurrences of thymine ("T") with uracil ("U"). Argument:

-   dna:A character string representing a DNA sequence (e.g., "ATGC")

```{r}
rna <- to_rna(dna)
print(f"The DNA sequence is: {dna}")
print(f"The RNA sequence is: {rna}")
```

## split_codons(rna, start)

This function takes a RNA sequence as input and converts it into a character vector where each component is a codon of 3 bases. Argument:

-   rna:A character string representing a RNA sequence (e.g., "AUGC")
-   start: An integer (1-3) that specifies the starting position for the reading frame within the RNA sequence

```{r}
codons <- split_codons(rna, start=1)
print(f"The RNA sequence is: {rna}")
print(f"The codons are: {codons}")
```

## to_protein()

The to_protein function takes the triplets sequences of RNA (codons) and translate them into its protein sequence. Argument:

-   codons: A character string representing a the codon sequences (e.g., "ATG", "UGG", "AUG")

```{r}
protein <- to_protein(codons)
print(f"The RNA sequence is: {rna}")
print(f"The codons are: {codons}")
print(f"The protein is: {protein}")
```

## dependencies()

Tras terminar de hacerlo debo ejecutar devtools::build_vignettes(): esto crea el pdf que tenemos que entregar el DTU learn

usethis::use_readme_rmd(open = TRUE) que crea el file README.Rdm: pegar el vignette y tal y cambiarlo a rmarkdown::github_document

luego runear devtools::build_readme() y y hacer un push en github
