---
title: "dogmolr"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{dogmolr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dogmolr)
```


### Introduction
The package "dogmolr" imitate the steps of the central dogma.

Specifically what is covered is the steps of transcription and translation.
By using the package it is possible to generate a DNA sequence and end op with a box plot showing the recurrences of the amino acids in the corresponding amino acid sequence.

The different functions in the package are meant to be used in a step by step fashion:
1. sample_nt_seq
2. dna_to_rna
3. r2c
4. transl_RNA_2_AA
5. plot_aa_freqs

You start by generating a DNA sequence, then transcribe it to RNA.
The RNA sequence is then split by another function into codons. The Codons are then translated to amino acids and lastly the frequencies of each appertaining amino acid can be plotted in a box plot. 

### Functions
## 1: sample_nt_seq
The functions is used to generate a DNA sequences of any length. 

# Example of usage
```{r}
dna_seq <- sample_nt_seq(30)
dna_seq
```

# Input arguments and expected output
Desired length of DNA sequence is taken as input, if non is given the standard length is set to 99.
Expected output is a DNA sting of given length.

## 2: dna_to_rna
Translate a DNA string into a RNA string

# Example of usage
```{r}
RNA_seq <- dna_to_rna(dna_seq)
RNA_seq
```

# Input arguments and expected output
The function input is a DNA string of anny length. 
Output is the resulting RNA string of given DNA segment. 

## 3: r2c
Splits an RNA string into subsisting's of its codons (e.g. ATG, GCC etc.). 

# Example of usage
```{r}
codons_vec <- r2c(RNA_seq)
codons_vec
```

# Input arguments and expected output
A RNA string is given as input, additionally the start posision for translation can be given (defult start position is 1).
The output is codons separated into individual strings. 

## 4: transl_RNA_2_AA
Translates list of codons into amino acids

# Example of usage
```{r}
AA_seq <- transl_RNA_2_AA(codons_vec)
AA_seq
```

# Input arguments and expected output
As input the function requress a string vector containing codons.
Output is a single string of the amino acids translated from the codons.

## 5: plot_aa_freqs
Plots the frequencies of amino acids as a box plot.

# Example of usage
```{r}
AA_freq_plot <- plot_aa_freqs(AA_seq)
AA_freq_plot
```

# Input arguments and expected output
Takes a string of amino acids.
Returns a box plot showing frequencies of the different amino acids in said string. 

### Use cases:

